Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment

### 2016-04-08 EMSOFT2016/paper.tex
update

\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
\numberofauthors{3}
\author{
\alignauthor
Takuro Yamamoto\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Wallamaloo, New Zealand}\\
       % \email{trovato@corporation.com}
\alignauthor
Hiroshi Oyama\\
    \affaddr{OKUMA Corporation}\\
    \affaddr{Aichi, JAPAN}
       % \affaddr{Dublin, Ohio 43017-6221}\\
       % \email{webmaster@marysville-ohio.com}
\alignauthor
Takuya Azumi\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Hekla, Iceland}\\
       % \email{larst@affiliation.org}
}
%\author{Takuro Yamamoto}
%\date{\today}

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\keywords{embedded software; script language; component based development;}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

An approach of efficient software development is to use component-based techniques.
CBD (Component-Based Development) is a design technique for constituting reusable components \cite{par:Crnkovic}.
Complex and large scale software systems can be developed efficiently using component-based techniques.
That is because software componentization provides high-reusability and easy verification.
It also makes a system flexible in extensions and specification changes.
There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems

In addition, another approach of efficient software development is to develop with script languages.
Most of current software are programmed in C language, and the development with C takes a high cost and more time to develop.
Script languages make software engineering more efficient and shorten a development period because script languages have high-productivity from their usability.
Java script, Perl, Python, Lua and Ruby are well-known as representative script languages.

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS} \cite{url:TOPPERS}.
mruby on TECS supports to effectively run mruby script language on embedded systems.
mruby on TECS also makes execution time 100 times faster than that of mruby.

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device to load mruby programs. 
%in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3}.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a periodic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.

{\mybf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\mybf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the continuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\mybf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
\item {\mybf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
\item {\mybf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

{\mybf Organization}: The paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows the system model of the proposed framework.
The bytecodes are transferred from the host to the target device with Bluetooth.
The RiteVMs and mruby library are assumed to be prepared in advance.
Each bytecode is allocated to a RiteVM, respectively.
Developers can run bytecodes transferred with Bluetooth in multitask.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/proposed.eps}
    \caption{System Model of the proposed framework}
    \label{fig:proposed}
\end{figure}

This section describes mruby on TECS on which the proposed framework is based.
mruby on TECS is a component-based framework for running script programs.
In mruby on TECS, two technologies are integrated: mruby and TECS.
To explain the system, mruby and TECS are also respectively described in this section.

\subsection{mruby}
\label{sec:mruby}
mruby is the light-weight implementation of Ruby programming language complying to part of the ISO standard.
Ruby is a object-oriented script language \cite{url:Ruby}.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar but also object-oriented functions such as classes and methods, exceptions, and garbage collection.

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
A RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.eps}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps increase productivity and reduce development duplication because the reusability of software is improved.
TECS also helps decrease complexity of the system because the generated component diagram can visualize the structure of whole software.

The component deployment and composition in TECS are statically performed, which gives optimization.
As a result, the overhead of execution time and memory consumption can be reduced.
There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\myit cell} which is an instance of a component in TECS consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
A {\myit entry} port is an interface to provide functions with other {\myit cell}s, and a {\myit call} port is an interface to use functions of other {\myit cell}s.
A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
Functions of a {\myit cell} are implemented in the C language.

A type of a {\myit entry}/{\myit call} port is defined by a {\myit signature} which is a set of functions.
A {\myit signature} is the interface definition of a {\myit cell}.
The {\myit call} port of a {\myit cell} can be connected to the {\myit entry} port of another {\myit cell} with the same {\myit signature}.
A {\myit celltype} is the definition of a {\myit cell}.
{\myit Celltype} defines one or more {\myit call}/{\myit entry} ports, attributes and internal variables.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Description}
The description of a component in TECS is divided into three parts, {\myit signature}, {\myit celltype}, and build description.
TECS code is written in .cdl (component description language) file.
The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.

\begin{description}
    \item[{\mybf Signature Description}]\mbox{}\\
        The {\myit signature} description defines an interface of a {\myit cell}.
        A {\myit signature} name is described following the keyword {\myit signature}.
        It also has the prefix ``s".
        In this way, a {\myit signature} is defined such as sMotor shown in Figure \ref{signature}.
        To make the definition of an interface clear, specifiers such as in and out are used in TECS.
        [in] and [out] represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor{
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\mybf Celltype Description}]\mbox{}\\
        The {\myit celltype} description defines {\myit entry} ports, {\myit call} ports, attributes, and valuables of a {\myit celltype}.
        An example of a {\myit celltype} description is shown in Figure \ref{celltype}.
        A {\myit celltype} name following the keyword {\myit celltype} with the prefix ``t" and elements of a {\myit celltype} is described.
        To define {\myit entry} ports, a {\myit signature} such as sMotor, and an {\myit entry} port name such as eMotor follow the keyword {\myit entry}.
        In the same way, {\myit call} ports can be defined.
        Attributes and valuables follow the keyword {\myit attr} and {\myit var} respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};
celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attribute;
    };
    var{
        int32_t variable;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\mybf Build Description}]\mbox{}\\
        The build description is used to instantiate {\myit cell}s and connect {\myit cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\myit celltype} name such as tMotor, and a {\myit cell} name such as Motor follow the keyword {\myit cell}.
        To compose {\myit cell}s, a {\myit call} port, a {\myit signature}, a {\myit entry} port in order are described.
        In this example, a {\myit entry} port eMotor in a {\myit cell} Motor is connected to a {\myit call} port cMotor in a {\myit cell} Caller.
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};
cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running script language.
This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}
The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge plays a role to call a native program (e.g. C legacy code) from an mruby program.
The mruby-TECS bridge provides native libraries for mruby.
It also gives TECS components to receive the invocation from an mruby program.
The mruby-TECS bridge is described in more detail bellow.

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.eps}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}
There is a great difference between the execution time of mruby and C language.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all codes.

The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of codes run quickly.

Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.eps}
    \caption{mruby-TECS Bridge}
    \label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates two things.
One is a {\myit celltype} to receive invocation from the mruby program.
The other is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.

A code of an mruby-TECS bridge is generated.
The generation code supports registration of classes and methods for mruby.
The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.

\section{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
The RiteVM reads the own bytecode and executes it.
The mruby applications run at the same time because of synchronization processing.
The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.eps}
    \caption{Detailed System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}

\subsection{mruby Bytecode Loader Using Bluetooth}
\label{sec:mruby bytecode loader using Bluetooth}
\footnote{
mruby bytecode loader is intended to improve the development efficiency, therefore software developers should use it for development phase.
Complete software should be compiled and linked in the storage/ROM device beforehand.
}
This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
Developers must rewrite the storage/ROM device every time the application programs are modified.
The OS on the target device should be also restarted.
It causes a low development efficiency to repeat that.
An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
%The work that an SD card is in and out needs to be done just once in the beginning.
Developers should just once carry out the work to connect the storage/ROM device and start the OS.

mruby programs are consisted of mruby application and libraries.
mruby application is the main code which software developers should program.
mruby libraries are the codes defining the functions for application such as Ruby classes. 
The mruby bytecodes including mruby application and libraries can be sent and run.
However, it is also wasteful in terms of the size and time to send bytecodes because libraries are not frequently modified. 
The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
Due to this design, RiteVMs can share the mruby libraries.
In addition, a RiteVM can use the own library that other RiteVMs should not use.

>>>>

\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
\numberofauthors{3}
\author{
\alignauthor
Takuro Yamamoto\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Wallamaloo, New Zealand}\\
       % \email{trovato@corporation.com}
\alignauthor
Hiroshi Oyama\\
    \affaddr{OKUMA Corporation}\\
    \affaddr{Aichi, JAPAN}\\
       % \affaddr{Dublin, Ohio 43017-6221}\\
       % \email{webmaster@marysville-ohio.com}
\alignauthor
Takuya Azumi\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Hekla, Iceland}\\
       % \email{larst@affiliation.org}
}
%\author{Takuro Yamamoto}
%\date{\today}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
In addition, multiple mruby programs can run cooperatively in the proposed framework.
Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\keywords{embedded software; scripting language; component-based development}
\section{Introduction}
Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
% Complex and large scale software systems can be developed efficiently using component-based techniques.
% That is because software componentization provides high-reusability.
Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
%It also visualize the entire system due to component diagrams, and makes a system flexible in extensions and specification changes.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.

%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
Moreover, mruby on TECS only supports a storage/ROM device for loading mruby programs.
Consequently, if mruby programs are modified, a secure digital (SD) card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart real-time operating systems (RTOSs) on the target device.
In addition, although mruby on TECS can support multiple virtual machines (multi-VMs), executing multiple tasks requires the developers to call the OS function.

This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
Note that RiteVM is the Ruby VM specifically designed for embedded systems.
The RiteVM scheduler manages the execution of multiple RiteVMs and allows developers to program multitasking more easily than the current version of mruby on TECS.

{\mybf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
\item {\mybf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\mybf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\mybf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\mybf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples.
\end{enumerate}

{\mybf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
    \vspace{0.5mm}
    \caption{System model of the proposed framework}
    \vspace{1mm}
    \label{fig:proposed}
\end{figure}

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows the system model of the proposed framework.
Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
Bytecodes transferred from the host via Bluetooth can run in multitask.

\subsection{mruby}
\label{sec:mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
    \vspace{0.5mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{1mm}
    \label{fig:mruby}
\end{figure}

\subsection{TECS}
\label{sec:TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    % \vspace{0.5mm}
    \caption{Component Diagram}
    \vspace{1mm}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\myit cell}, which is an instance of a component in TECS, consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
An {\myit entry} port is an interface that provides functions to other {\myit cell}s, and a {\myit call} port is an interface that enables the use of other {\myit cell}'s functions.
A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
{\myit Cell} functions are implemented in C.

The type of {\myit entry}/{\myit call} port is defined by a {\myit signature}, which is a set of functions.
A {\myit signature} is the interface definition of a {\myit cell}.
The {\myit cell}'s  {\myit call} port can be connected to the {\myit entry} port of another {\myit cell} by the same {\myit signature}.
Here, {\myit celltype} defines one or more {\myit call}/{\myit entry} ports, attributes, and internal variables of a {\myit cell}.

\subsubsection{Component Description}
In TECS, components are described by {\myit signature}, {\myit celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

\begin{description}
    \item[{\mybf Signature Description}]\mbox{}\\
        The {\myit signature} defines a {\myit cell} interface.
        The {\myit signature} name follows the keyword {\myit signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\vspace{1mm}
\caption{Signature Description}
\vspace{1mm}
\label{signature}
\end{figure}
    \item[{\mybf Celltype Description}]\mbox{}\\
        The {\myit celltype} defines {\myit entry} ports, {\myit call} ports, attributes, and variables.
        A {\myit celltype} name with the prefix ``t'' follows the keyword {\myit celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\myit entry} ports, a {\myit signature}, e.g., sMotor, and an {\myit entry} port name, e.g., eMotor, follow the keyword {\myit entry}.
        {\myit Call} ports are defined similarly.
        Attributes and variables follow the keywords {\myit attr} and {\myit var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\vspace{1mm}
\caption{Celltype Description}
\vspace{1mm}
\label{celltype}
\end{figure}
    \item[{\mybf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\myit cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\myit celltype} name and {\myit cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\myit cell}.
        To compose {\myit cell}s, a {\myit call} port, {\myit cell}'s name, and an {\myit entry} port are described in that order.
        In Figure \ref{build}, {\myit entry} port eMotor in {\myit cell} Motor is connected to {\myit call} port cMotor in {\myit cell} Caller.
        {\myit C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\vspace{1mm}
\caption{Build Description}
\vspace{1mm}
\label{build}
\end{figure}

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
% mruby on TECS is a component-based framework for running script language.
% This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}
The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% The mruby-TECS bridge is described in more detail bellow.

In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
    \vspace{0.5mm}
\caption{System model of existing mruby on TECS}
    \vspace{1mm}
\label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.

Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
    \vspace{0.5mm}
\caption{mruby-TECS bridge}
    \vspace{1mm}
\label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates a {\myit celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.

\section{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
The RiteVM reads the transferred bytecode and executes it with libraries.
The mruby applications run simultaneously due to synchronized processing.
The RiteVM scheduler switches RiteVM tasks because multiple tasks can run concurrently.
The following subsection explains these functionalities.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
    \vspace{0.5mm}
\caption{Detailed system model of the proposed framework}
    \vspace{1mm}
\label{fig:system_model}
\end{figure}

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader, for mruby bytecode.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.

mruby programs consist of an mruby application and mruby libraries.
An mruby application is the main program code, mruby libraries define the functions for the application, such as Ruby classes. 
The mruby bytecodes including both an mruby application and mruby libraries can be transferred and executed on the target device.
However, this is also wasteful in terms of bytecode size and the time required to transfer the bytecodes, because the libraries are not modified frequently.
With the proposed framework, only mruby applications are transferred, and the mruby libraries are preserved on the storage/ROM device beforehand.
As a result, RiteVMs can share mruby libraries.
In addition, a RiteVM can use its own library, which other RiteVMs should not use.
